Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-07-14 draftfinalreport_v4.Rnw
Generate the table of proportion naive in each age group rather than having it copy n pasted

\begin{table}[htdp]\small % saved as vaccine_proportions_Cohort
\begin{center}
\begin{tabular}{lrrrr}
\hline
Age range (yrs) & Proportion of na\"{\i}ve population\\
\hline
2--5 & 0.04\\
5--11 & 0.15\\
5--16 & 0.27\\
5--18 & 0.31\\
11--16 & 0.14\\
11--18 & 0.18\\
19--25 & 0.19\\
19--30 & 0.34\\
19--46 & 0.46\\
0--29 & 0.72\\
0--44 & 0.89\\
>8 & 0.8 \\ 
\hline
\end{tabular}
\end{center}
\caption{Proportion of the currently na\"{\i}ve New Zealand population that would be immunised if all na\"{\i}ve people in each age range were immunised. The estimated additional proportion of the population requiring immunisation is 28\%}
\label{table:coh_vac}
\end{table}%

>>>>

\begin{table}[hbtp] \scriptsize
\captionsetup{width=1\textwidth}
<<results=tex,echo=FALSE>>=
colnames(propvCohort)<-c("Age range (yrs)","Proportion naive")
latex(propvCohort, file="", table.env=FALSE,rowname=NULL)
@
\caption{Proportion of the currently na\"{\i}ve New Zealand population that would be immunised if all na\"{\i}ve people in each age range were immunised. The estimated additional proportion of the population requiring immunisation is 28\%}
\label{table:coh_vac}
\end{table}
